Growth Resilience

### 2017-09-15 analysis/analysis_resilience_bai.Rmd
update
change letters and update tables

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

@@

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

@@

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

@@

cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01)
cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01)
cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01)
```

@@

mhuber <- rbind(rarc$mest, rart$mest, rars$mest, rarrs$mest)
mhuber %>% pander()
```

@@

mhuber_a <- rbind(rarc$mest_a, rart$mest_a, rars$mest_a, rarrs$mest_a)
mhuber_a %>% pander()
```

@@

mhuber_b <- rbind(rarc$mest_b, rart$mest_b, rars$mest_b, rarrs$mest_b)
mhuber_b %>% pander()
```

@@

```{r}
# Export data 
write.csv(mhuber, file=paste0(di, '/out/anovas_resilience/robust_mhuber.csv'), row.names = F)
write.csv(mhuber_a, file=paste0(di, '/out/anovas_resilience/robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_b, file=paste0(di, '/out/anovas_resilience/robust_mhuber_b.csv'), row.names = F)

>>>>

letraArs <- cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01) %>% mutate(var ='rs')
letraArs

letraBrs <- cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01) %>% mutate(var ='rs')
letraBrs # Manual (IMPROVE IT)
letraBrs <- data.frame(Group = c('SJ', 'caH', 'caL'),
                     Letter = c('a','a','a'),
                     MonoLetter = c('a','a','a')) %>% mutate(var ='rs')
letraBrs

letraABrs  <- cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01) %>% mutate(var ='rs')
letraABrs

@@

letraArc <- cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01) %>% mutate(var ='rc')
letraArc
letraBrc <- cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01) %>% mutate(var ='rc')
letraBrc
letraABrc <- cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01) %>% mutate(var ='rc')
letraABrc

@@

letraArt <- cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraArt #Manual (IMPROVE IT)
letraArt <- data.frame(Group = as.factor(c('25', '212')),
                     Letter = as.factor(c('a','a')),
                     MonoLetter = as.factor(c('a','a'))) %>% mutate(var ='rt')
letraBrt <- cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraBrt
letraABrt <- cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01) %>% mutate(var ='rt')
letraABrt 
```

@@

letraArrs <- cldList(comparison = x$pha$Comparison, p.value = x$pha$p.adjust, threshold  = 0.01) %>% mutate(var ='rrs')
letraArrs
letraBrrs <- cldList(comparison = x$phb$Comparison, p.value = x$phb$p.adjust, threshold  = 0.01) %>% mutate(var ='rrs')
letraBrrs
letraABrrs <- cldList(comparison = x$phab$Comparison, p.value = x$phab$p.adjust, threshold  = 0.01) %>% mutate(var ='rrs')
letraABrrs 
```

```{r}

letrasA <- rbind(letraArs, letraArc, letraArt, letraArrs) %>% 
  mutate(disturb_year = 
           case_when(Group == "25" ~ "2005",
                     Group == "212" ~ "2012")) %>% 
  dplyr::select(-Group)

letrasB <- letrasB %>% rename(site = Group)

letrasAB <- rbind(letraABrs, letraABrc, letraABrt, letraABrrs) %>% 
  separate(Group, into=c('disturb_year', 'site')) %>% 
  mutate(disturb_year = 
           case_when(disturb_year == "25" ~ "2005",
                     disturb_year == "212" ~ "2012"))
```

@@

mhuber <- rbind(rarc$mest, rart$mest, rars$mest, rarrs$mest)

# add letras 
mhuber <- mhuber %>% inner_join(letrasAB, by=c('var','disturb_year', 'site'))

mhuber_agg <- mhuber %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite_("ci", c("lower.ci", "upper.ci"), sep=",") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  dplyr::select(-MonoLetter) %>% 
  dplyr::select(var, disturb_year:ci, Letter) %>% as.data.frame()

mhuber_agg %>% pander() 
```

@@

mhuber_a <- rbind(rarc$mest_a, rart$mest_a, rars$mest_a, rarrs$mest_a)
mhuber_a <- mhuber_a %>% inner_join(letrasA, by=c('var','disturb_year'))

mhuber_agg_a <- mhuber_a %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite_("ci", c("lower.ci", "upper.ci"), sep=",") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  dplyr::select(-MonoLetter) %>% 
  dplyr::select(var, disturb_year:ci, Letter) %>% as.data.frame()

mhuber_agg_a %>% pander()

@@

mhuber_b <- rbind(rarc$mest_b, rart$mest_b, rars$mest_b, rarrs$mest_b)
mhuber_b <- mhuber_b %>% inner_join(letrasB, by=c('var','site'))

mhuber_agg_b <- mhuber_b %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite_("ci", c("lower.ci", "upper.ci"), sep=",") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  dplyr::select(-MonoLetter) %>% 
  dplyr::select(var, site:ci, Letter) %>% as.data.frame()

mhuber_agg_b %>% pander() 
```

@@

```{r}
# Export data 
write.csv(mhuber, file=paste0(di, '/out/anovas_resilience/robust_mhuber.csv'), row.names = F)
write.csv(mhuber_agg, file=paste0(di, '/out/anovas_resilience/robust_mhuber_agg.csv'), row.names = F)
write.csv(mhuber_a, file=paste0(di, '/out/anovas_resilience/robust_mhuber_a.csv'), row.names = F)
write.csv(mhuber_agg_a, file=paste0(di, '/out/anovas_resilience/robust_mhuber_agg_a.csv'), row.names = F)
write.csv(mhuber_b, file=paste0(di, '/out/anovas_resilience/robust_mhuber_b.csv'), row.names = F)
write.csv(mhuber_agg_b, file=paste0(di, '/out/anovas_resilience/robust_mhuber_agg_b.csv'), row.names = F)
